---
title       : Exploratory Data Analysis 
subtitle    : mtcars
author      : Weiwei
job         : Data Science
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [mathjax]            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Goals:
1. Correclation matrix among selected variables
2. Boxplot of selected variables
3. Summary table of selected variables

--- 

## The description of mtcars and summary table
The data was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973–74 models).

```{r echo=FALSE}
library(ggplot2)
library(corrplot)
library(reshape2)
library(clusterSim)
data(mtcars)
data <- mtcars
matrix <- data.frame(data$disp, data$mpg,data$cyl,data$hp)
```

```{r}
summary(matrix)
```

---

## The correlaction matrix



```{r}
corr_matrix <- cor(matrix)
corrplot.mixed(corr_matrix, order="AOE", upper="circle",tl.pos="lt",tl.col="black", tl.cex=1, tl.srt=0, diag = "u" )

```


---

## The boxplot
```{r echo=FALSE}
dat <-data.Normalization(matrix,type="n1",normalization="column");dat <- melt(dat)
ggplot(dat, aes(x=variable, y=value,fill=variable))+geom_boxplot()
```

---








